### 2017-12-05 manuscript.rmd
updated file name to figures raw

	p_phylogram = ggtree( species_tree ) +
			# geom_text( aes( label=support ), vjust=-.5, hjust=1, size=2.5, col="darkslategray4" ) +
	    geom_text(aes(label=get_node_support(species_tree, bootstrap_trees)), vjust=-.5, hjust=1, size=2.5, col="red") +
      geom_text(aes(label=get_node_support(species_tree, phylobayes_trees)), vjust=1.5, hjust=1, size=2.5, col="blue") +
			geom_tiplab( size=3 ) +
			xlim( NA, 4 ) +
			geom_cladelabel( node=cystonectae_node, label="Cystonectae", align=FALSE, offset=1, color='red' ) +
			geom_cladelabel( node=calycophora_node, label="Calycophora", align=FALSE, offset=1, color='blue' ) +
			geom_strip(
				which( species_tree$tip.label=="Agalma elegans" ),
				which( species_tree$tip.label=="Apolemia white" ),
				barsize=0.5,
				color='orange',
				offset=1,
				label='"Physonectae"'
			) +
			geom_strip(
				which( species_tree$tip.label=="Hydractinia symbiolongicarpus" ),
				which( species_tree$tip.label=="Nematostella vectensis" ),
				barsize=0.5,
				color='gray',
				offset=1,
				label='"Outgroups"'
			)
#These are commented out to avoid outputting the figure on every knit (remove comment to generate)

#	pdf("figures_for_AI/figure_3_raw.pdf")
#	flip( p_phylogram, euphysonectae_node, calycophora_node )
#	dev.off()

@@

#Simmap SEX
#plotTree(ultratree, lwd = 4)
#colors = c("black", "red")
#names(colors) = c("Dioecious", "Monoecious")
#sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
#nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
#add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
# pdf("figures_for_AI/density_sex_sim.pdf")
# densityMap(sex_sim)
# dev.off()
```

@@

# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
# pdf("figures_for_AI/palpons_sim.pdf")
# densityMap(palpons_sim)
# dev.off()
```

@@

# pdf("figures_for_AI/trimmed_violinVars.pdf")
# ggplot(trimmed_SDdata, aes(x = Species, y=-Depth)) + geom_violin() + theme_classic()
# dev.off()
```

@@

# pdf("figures_for_AI/overview_ggheatmap_chars.pdf")
# gheatmap(p, f_cdata, offset = 0.4, width=0.5, colnames_position = 'top', font.size = 1)
# dev.off()
```

@@

```{r median_cont_BWincluded, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species including blue water diving observations."}
median_aggregate = aggregate(trimmed_SDdata$Depth,by=list(trimmed_SDdata$Species), FUN=median)
names(median_aggregate) = c("Spp","Depth")
median_aggregate[33,2] = 0
median_aggregate = median_aggregate[match(median_aggregate$Spp, ultratree$tip.label),]
median_depth = median_aggregate$Depth
names(median_depth) = median_aggregate$Spp
depthmap <- contMap(ultratree, median_depth, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

>>>>

	p_phylogram = ggtree( species_tree ) +
			# geom_text( aes( label=support ), vjust=-.5, hjust=1, size=2.5, col="darkslategray4" ) +
	    geom_text(aes(label=get_node_support(species_tree, bootstrap_trees)), vjust=-.5, hjust=1, size=2.5, col="red") +
      geom_text(aes(label=get_node_support(species_tree, phylobayes_trees)), vjust=1.5, hjust=1, size=2.5, col="blue") +
			geom_tiplab( size=3 ) +
			xlim( NA, 4 ) +
			geom_cladelabel( node=cystonectae_node, label="Cystonectae", align=FALSE, offset=1, color='red' ) +
			geom_cladelabel( node=calycophora_node, label="Calycophora", align=FALSE, offset=1, color='blue' ) +
			geom_strip(
				which( species_tree$tip.label=="Agalma elegans" ),
				which( species_tree$tip.label=="Apolemia white" ),
				barsize=0.5,
				color='orange',
				offset=1,
				label='"Physonectae"'
			) +
			geom_strip(
				which( species_tree$tip.label=="Hydractinia symbiolongicarpus" ),
				which( species_tree$tip.label=="Nematostella vectensis" ),
				barsize=0.5,
				color='gray',
				offset=1,
				label='"Outgroups"'
			)

pdf("figures_raw/figure_3_raw.pdf")
flip( p_phylogram, euphysonectae_node, calycophora_node )
dev.off()

@@

#Simmap SEX
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
 pdf("figures_raw/figure_5_raw_sex.pdf")
 densityMap(sex_sim)
 dev.off()
```

@@

 plotTree(ultratree, lwd = 4)
 colors = c("black", "red")
 names(colors) = c("Absent", "Present")
 palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
 nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
 add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
 pdf("figures_raw/figure_5_raw_palpons.pdf")
 densityMap(palpons_sim)
 dev.off()
```

@@

 pdf("figures_raw/figure_4_raw_violin.pdf")
 ggplot(trimmed_SDdata, aes(x = Species, y=-Depth)) + geom_violin() + theme_classic()
 dev.off()
```

@@

 pdf("figures_raw/figure_4_raw_heat.pdf")
 gheatmap(p, f_cdata, offset = 0.4, width=0.5, colnames_position = 'top', font.size = 1)
 dev.off()
```

@@

 ```{r median_cont_BWincluded, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species including blue water diving observations."}
# median_aggregate = aggregate(trimmed_SDdata$Depth,by=list(trimmed_SDdata$Species), FUN=median)
# names(median_aggregate) = c("Spp","Depth")
# median_aggregate[33,2] = 0
# median_aggregate = median_aggregate[match(median_aggregate$Spp, ultratree$tip.label),]
# median_depth = median_aggregate$Depth
# names(median_depth) = median_aggregate$Spp
# depthmap <- contMap(ultratree, median_depth, plot=F) %>% setMap(colors=c("cyan","blue","black"))
# plot(depthmap)
```
